---
title: "Complex Network"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    css: ./style.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(extrafont)
source(file = "./scripts/pre_needed_functions.R")
source(file = "./scripts/homework1.R")
source(file = "./scripts/homework2.R")
source(file = "./scripts/homework3.R")
source(file = "./scripts/homework3_2.R")
source(file = "./scripts/homework4.R")
```

Homework 1 {.storyboard}
===
### A) Erdos Renyi Graph

```{r}
drawGraph(erdosRenyiGraph, homework1Layout)
```

### B) Complemente

``` {r}
drawGraph(complementeryGraph, homework1Layout)
```


### C) Adjecency Materix
Matrix
```{r}
erdosRenyiMatrix
```

### D) Some powers of the matrix
Matrix^2
```{r}
erdosRenyiMatrixPow2
```
Matrix^5
```{r}
erdosRenyiMatrixPow5
```
Matrix^15
```{r}
erdosRenyiMatrixPow15
```
Matrix^30
```{r}
erdosRenyiMatrixPow30
```

### E) Radius, Diameter and Girth
Eccentricity
``` {r}
eccentricityErdosReyniGraph
```
Radius
``` {r}
radiusErdosReyniGraph
```
Diameter
``` {r}
diameterErdosReyniGraph
```
Girth
``` {r}
girthErdosReyniGraph
```

### F) Density
Density
``` {r}
density
```


### G) Induced Graph
```{r}
drawGraph(inducedErdosRenyiGraph, homework1InducedGraphLayout)
```

### H)degree, pathesLength, edge avarage
degree's average
``` {r}
degreeAvarage
```
avarage of pathes length
``` {r}
avarageShortestPaths
```
edge's avarage
``` {r}
edgesAvarage
```

### I)clustering coefficient
local clustering coefficient
``` {r}
localClusteringCoefficient
```
global clustering coefficient
``` {r}
globalClusteringCoefficient
```

Homework 2 {.storyboard}
===

### A)erdosRenyi Graph With Direction

``` {r}
drawGraph(erdosRenyiGraphWithDirection, homework1Layout)
```

### B)Transposed

```{r}
drawGraph(erdosRenyiGraphWithDirectionTransposed, homework1Layout)
```


### C)Subdivision Graph
```{r}
drawGraph(subdivisionGraph, layout.auto(subdivisionGraph))
```

***
```{r}
E(subdivisionGraph)
```


### D)Hamiltonian Cycle
```{r}
#hamiltonianEdges
#drawGraph(hamiltonianGraph, homework1Layout)
```

### E)Adjecency Matrix
```{r}
erdosRenyiMatrixWithDirection
```

### F)Radius, Diameter and Girth
Eccentricity
``` {r}
eccentricityErdosReyniGraphWithDirection
```
Radius
``` {r}
radiusErdosReyniGraphWithDirection
```
Diameter
``` {r}
diameterErdosReyniGraphWithDirection
```
Girth
``` {r}
girthErdosReyniGraphWithDirection
```

### G)Induced Graph
```{r}
drawGraph(inducedErdosRenyiGraphWithDirection, homework2InducedGraphLayout)
```

### H)degree, pathesLength, edge avarage
degree's average
``` {r}
degreeAvarageDirected
```
avarage of pathes length
``` {r}
avarageShortestPathsDirected
```
edge's avarage
``` {r}
edgesAvarageDirected
```
### I)clustering coefficient
local clustering coefficient
``` {r}
localClusteringCoefficientDirected
```
global clustering coefficient
``` {r}
globalClusteringCoefficientDirected
```
Homework 3 {.storyboard}
===


### A)erdosRenyi Graph With Direction and wieght
```{r}
headCollection
#plot(erdosRenyiGraphWithDirectionAndWeighted, edge.arrow.size=.3, layout = homework1Layout)
drawGraph(erdosRenyiGraphWithDirectionAndWeighted, homework1Layout)
```

### B)subGraph

```{r}
drawGraph(subEderdosRenyiGraphWithDirectionAndWeighted,homework1Layout)
headCollectionOfSubGraph
#plot(subEderdosRenyiGraphWithDirectionAndWeighted, edge.arrow.size=.3, layout = homework1Layout)

```

### C)MST

```{r}
headCollectionOfMST
#plot(MSTOfErdosRenyiGraphWithDirectionAndWeighted, edge.arrow.size=.3, layout = homework1Layout)
drawGraph(MSTOfErdosRenyiGraphWithDirectionAndWeighted, homework1Layout)
```

### D) Radius, Diameter, Girth

Eccentricity
``` {r}
eccentricityerdosRenyiGraphWithDirectionAndWeighted
```
Radius
``` {r}
radiuserdosRenyiGraphWithDirectionAndWeighted
```
Diameter
``` {r}
diametererdosRenyiGraphWithDirectionAndWeighted
```
Girth
``` {r}
girtherdosRenyiGraphWithDirectionAndWeighted
``` 


### E)degree, pathesLength, edge avarage
degree's average
``` {r}
degreeAvarageDirectedWithWeight
```
avarage of pathes length
``` {r}
avarageShortestPathsDirectedWithWeight
```
edge's avarage
``` {r}
edgesAvarageDirectedWithWeight
```

### F)clustering coefficient
local clustering coefficient
``` {r}
localClusteringCoefficientDirectedWithWeight
```
global clustering coefficient
``` {r}
globalClusteringCoefficientDirectedWithWeight
```

Homework 4 {.storyboard}
===

### A) Multi Graph

```{r}
drawGraph(multiGraph, homework1Layout) 
```


### B)degree, pathesLength, edge avarage
degree's average
``` {r}
degreeAvarageMultiGraph
```
avarage of pathes length
``` {r}
avarageShortestPathsMultiGraph
```
edge's avarage
``` {r}
edgesAvarageMultiGraph
```

### C)clustering coefficient
local clustering coefficient
``` {r}
localClusteringCoefficientMultiGraph
```
global clustering coefficient
``` {r}
globalClusteringCoefficientMultiGraph
```

Homework 5 {.storyboard}
===

### A) Watts Strogatz Graph With 30 Node

```{r}
drawGraph(wattzStrogatzGraph, homework1Layout) 
```


### B)degree, pathesLength, edge avarage
degree's average
``` {r}
#degreeAvarageWattzStrogatzGraph
```
avarage of pathes length
``` {r}
#avarageShortestPathsWattzStrogatzGraph
```
edge's avarage
``` {r}
#edgesAvarageWattzStrogatzGraph
```

### C)clustering coefficient
local clustering coefficient
``` {r}
#localClusteringCoefficientWattzStrogatzGraph
```
global clustering coefficient
``` {r}
#globalClusteringCoefficientWattzStrogatzGraph
```
### D) Watts Strogatz Graph With 300 Node

```{r}
drawGraph(wattzStrogatzGraphWith300Node, homework1Layout) 
```
