---
title: "Complex Network"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    css: ./style.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(extrafont)
source(file = "./scripts/pre_needed_functions.R")
source(file = "./scripts/homework1.R")
source(file = "./scripts/homework2.R")
source(file = "./scripts/homework3.R")
source(file = "./scripts/homework4.R")
```

Homework 1 {.storyboard}
===
### A) Erdos Renyi Graph

```{r}
drawGraph(erdosRenyiGraph, homework1Layout)
```

### B) Complemente

``` {r}
drawGraph(complementeryGraph, homework1Layout)
```


### C) Adjecency Materix
Matrix
```{r}
erdosRenyiMatrix
```

### D) Some powers of the matrix
Matrix^2
```{r}
erdosRenyiMatrixPow2
```
Matrix^5
```{r}
erdosRenyiMatrixPow5
```
Matrix^15
```{r}
erdosRenyiMatrixPow15
```
Matrix^30
```{r}
erdosRenyiMatrixPow30
```

### E) Radius, Diameter and Girth
Eccentricity
``` {r}
eccentricityErdosReyniGraph
```
Radius
``` {r}
radiusErdosReyniGraph
```
Diameter
``` {r}
diameterErdosReyniGraph
```
Girth
``` {r}
girthErdosReyniGraph
```

### F) Density
Density
``` {r}
density
```


### G) Induced Graph
```{r}
drawGraph(inducedErdosRenyiGraph, homework1InducedGraphLayout)
```


Homework 2 {.storyboard}
===

### A)erdosRenyi Graph With Direction

``` {r}
erdosRenyiGraphWithDirectionInputDegree
``` 

``` {r}
drawGraph(erdosRenyiGraphWithDirection, homework1Layout)
```

### B)Transposed

```{r}
drawGraph(erdosRenyiGraphWithDirectionTransposed, homework1Layout)
```


### C)Subdivision Graph
```{r}
drawGraph(subdivisionGraph, layout.fruchterman.reingold(subdivisionGraph))
```

***
```{r}
E(subdivisionGraph)
```


### D)Hamiltonian Cycle
```{r}

```

### E)Adjecency Matrix
```{r}
erdosRenyiMatrixWithDirection
```

### F)Radius, Diameter and Girth
Eccentricity
``` {r}
eccentricityErdosReyniGraphWithDirection
```
Radius
``` {r}
radiusErdosReyniGraphWithDirection
```
Diameter
``` {r}
diameterErdosReyniGraphWithDirection
```
Girth
``` {r}
girthErdosReyniGraphWithDirection
```

### G)Induced Graph
```{r}
drawGraph(inducedErdosRenyiGraphWithDirection, homework2InducedGraphLayout)
```

Homework 3 {.storyboard}
===


### A)
```{r}
headCollection
plot(erdosRenyiGraphWithDirectionAndWeighted, edge.arrow.size=.3, layout = homework1Layout)

```

### B)subGraph

```{r}
plot(subEderdosRenyiGraphWithDirectionAndWeighted, edge.label=E(subEderdosRenyiGraphWithDirectionAndWeighted)$label, edge.arrow.size=.3, layout = homework1Layout)

```

### C)MST

```{r}
drawGraph(MSTOfErdosRenyiGraphWithDirectionAndWeighted, homework1Layout)
```

### D) Radius, Diameter, Girth

Eccentricity
``` {r}
eccentricityerdosRenyiGraphWithDirectionAndWeighted
```
Radius
``` {r}
radiuserdosRenyiGraphWithDirectionAndWeighted
```
Diameter
``` {r}
diametererdosRenyiGraphWithDirectionAndWeighted
```
Girth
``` {r}
girtherdosRenyiGraphWithDirectionAndWeighted
``` 

Homework 4 {.storyboard}
===

### A) Multi Graph

```{r}
drawGraph(multiGraph, homework1Layout) 
```

